---
title: "Detailed Policy Tools for COVID-19 in Saskatchewan"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
---

```{r setup, include=FALSE}
library(flexdashboard)
library(readr)
library(dygraphs)
library(xts)
library(zoo)
source('./utils.R')

indata <- readr::read_csv('./data/cases-sk.csv')
cases <- xts(indata$Cases, order.by=indata$Date)
colnames(cases) <- c('Cases')
```

### Comparing per capita cases across Canada from first case

```{r}
load('./data/cacheData.RData')
ab <- tsA[which(tsA$Province.State == 'Alberta'),]
bc <- tsA[which(tsA$Province.State == 'British Columbia'),]
on <- tsA[which(tsA$Province.State == 'Ontario'),]
sk <- tsA[which(tsA$Province.State == 'Saskatchewan'),]
it <- tsA[which(tsA$Country.Region == 'Italy'),]

xtsDta <- cbind(
  bc=convertTs(bc),
  ab=convertTs(ab),
  sk=convertTs(sk),
  on=convertTs(on),
  it=convertTs(it)
)
aa <- alignDf(xtsDta)

popn <- data.frame(
  on = 14.57,
  sk = 1.174,
  ab = 4.371,
  bc = 5.071,
  it = 60.48
)

pc <- ts(data.frame(
  on=aa$on/popn$on,
  sk=aa$sk/popn$sk,
  ab=aa$ab/popn$ab,
  bc=aa$bc/popn$bc,
  it=aa$it/popn$it
))
dygraph(pc, main='Cases per capita from first case')
```

*** 

There has been a slower per-capita exponential growth period in Saskatchewan, when compared to other regions.

### Comparing per capita deaths across Canada from first case {data-commentary-width=400}

```{r}
load('./data/cacheData.RData')
abd <- tsD[which(tsD$Province.State == 'Alberta'),]
bcd <- tsD[which(tsD$Province.State == 'British Columbia'),]
ond <- tsD[which(tsD$Province.State == 'Ontario'),]
skd <- tsD[which(tsD$Province.State == 'Saskatchewan'),]
itd <- tsD[which(tsD$Country.Region == 'Italy'),]

xtsDtaD <- cbind(
  bc=convertTs(bcd),
  ab=convertTs(abd),
  sk=convertTs(skd),
  on=convertTs(ond),
  it=convertTs(itd)
)

popn <- data.frame(
  on = 14.57,
  sk = 1.174,
  ab = 4.371,
  bc = 5.071,
  it = 60.48
)

pcd <- ts(data.frame(
  on=xtsDtaD$on/popn$on,
  sk=xtsDtaD$sk/popn$sk,
  ab=xtsDtaD$ab/popn$ab,
  bc=xtsDtaD$bc/popn$bc
))
dygraph(pcd[, c('sk', 'ab', 'bc', 'on')], main='Deaths per capita from first case') 
```
*** 

Deaths comparison aligned.


### Comparing per capita deaths across Canada from first case {data-commentary-width=400}

```{r}
gr <- 100*diff(cases)/c(NA,cases[1:(nrow(cases)-1)])
names(gr) <- 'Growth'
# dygraph(dta, main = "Official COVID-19 Cases in Saskatchewan") %>%
#   dySeries("InferredCases", axis = "y2")
dygraph(gr, main = "Growth rate of confirmed cases") %>%
  dyLimit(7, label = '5-day doubling', color = "orange") %>%
  dyLimit(5, label = '10-day doubling', color = 'red')
```
*** 

Deaths comparison aligned.


<!-- ```{r} -->
<!-- itt <- data.frame(cases=xtsDta$it/popn$it, deaths=xtsDtaD$it/popn$it) -->
<!-- names(itt) <- c('cases', 'deaths') -->
<!-- dygraph(ts(itt), main='Cases and deaths per capita (Italy)') %>% -->
<!--   dySeries("deaths", axis = "y2") -->
<!-- ``` -->

<!-- ```{r} -->
<!-- itt <- data.frame(cases=xtsDta$on/popn$on, deaths=xtsDtaD$on/popn$on) -->
<!-- names(itt) <- c('cases', 'deaths') -->
<!-- dygraph(ts(itt), main='Cases and deaths per capita (Ontario)') %>% -->
<!--   dySeries("deaths", axis = "y2") -->
<!-- ``` -->

